Equation-of-state insensitive relations after GW170817

### 2019-02-19 paper/bin-love-after-gw170817.tex
fixed caption of Fig. 2

Figure~\ref{fig:stackedFisher} shows this result in more detail. We here present the (Fisher-estimated) statistical uncertainty in the measurement of $\lambda_{0}$ with various detectors (O2~\cite{aLIGO}, aLIGO~\cite{aLIGO}, A\texttt{+}~\cite{Ap_Voyager_CE}, Voyager~\cite{Ap_Voyager_CE}, ET~\cite{ET}, CE~\cite{Ap_Voyager_CE}) for an event identical to GW170817. The x-axis shows the signal-to-noise ratio for a GW170817 event detected with each of these detectors. We also present the combined statistical uncertainty $\sigma^A_N$ after $N$ detections with each of these instruments, with the top and bottom of the region representing the most optimistic and pessimistic expectation for the number of detections expected from the binary NS merger rate (see also Table~\ref{tab:variances}). These statistical uncertainties should be compared to the systematic uncertainty in $\lambda_{0}$ due to EoS-variability improved with the constrained set. Observe that the statistical and the systematic uncertainties cross for Voyager-class detectors. s

@@

\begin{figure}
\begin{center} 
\includegraphics[width=\columnwidth]{EoSs.eps}
\end{center}
\caption{
Small representative sets of the unconstrained (dotted) and constrained (solid) EoSs used in this analysis. 
The constrained EoSs were populated by randomly selecting 100 posterior samples obtained from the GW170817 90\% credible level shown in cyan~\cite{LIGO:posterior}.
Additionally, 100 unconstrained EoSs were generated by randomly sampling spectral coefficients of physically valid EoSs, with no further constraints applied.
The following restrictions were also applied to both sets of EoSs: (i) each EoS must have a causal structure within 10\%, and (ii) each EoS must support a maximum NS mass of at least $1.97 \text{ M}_{\odot}$, consistent with astrophysical observations.
Finally, the high density core EoSs generated above were stitched to the low-density crust EoS of SLy~\cite{Douchin:2001sv} at $\rho_{\text{stitch}}=1.3 \times 10^{14} \text{ g/cm}^3$.}
\label{fig:eos}
\end{figure}

>>>>

Figure~\ref{fig:stackedFisher} shows this result in more detail. We here present the (Fisher-estimated) statistical uncertainty in the measurement of $\lambda_{0}$ with various detectors (LIGO O2~\cite{aLIGO}, Advanced LIGO (aLIGO)~\cite{aLIGO}, LIGO A\texttt{+} (A\texttt{+})\cite{Ap_Voyager_CE}, Voyager~\cite{Ap_Voyager_CE}, the Einstein Telescope (ET)~\cite{ET}, and the Cosmic Explorer (CE)~\cite{Ap_Voyager_CE}) for an event identical to GW170817. The x-axis shows the signal-to-noise ratio for a GW170817 event detected with each of these detectors. We also present the combined statistical uncertainty $\sigma^A_N$ after $N$ detections with each of these instruments, with the top and bottom of the region representing the most optimistic and pessimistic expectation for the number of detections expected from the binary NS merger rate (see also Table~\ref{tab:variances}). These statistical uncertainties should be compared to the systematic uncertainty in $\lambda_{0}$ due to EoS-variability improved with the constrained set. Observe that the statistical and the systematic uncertainties cross for Voyager-class detectors.

@@

\begin{figure}
\begin{center} 
\includegraphics[width=\columnwidth]{EoSs.eps}
\end{center}
\caption{(Color Online) Small representative samples of the unconstrained (dotted) and constrained (solid) sets, together with the 90\% marginalized posterior distribution from the observation of GW170817 (cyan shaded region)~\cite{LIGO:posterior}. Observe that the there is significantly less variability in the constrained set of EoSs due to the requirement that they be consistent with the GW170817 observation.}
\label{fig:eos}
\end{figure}
